Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-21 paper/Draft.tex
Ready to plot histograms of revision in fore casts and uncertainty.

@@

>>>>

Figure \ref{UnceratitnyOtherMoments} plots the population uncertainty asgainst forecast errors and disagreements.

Once implication from FIRE is that all individuals not only agree on mean but also share same degree of uncertainty. While in fact, we observe long-lasting heterogeneity in uncertainty both from professional forecasters and households. Figure \ref{IQR_Unceratitny} show that there is  not only dispersion of individual forecasts i.e. disagreements, but alslo great heterogeneity in uncertainty. One stylized fact from these observations is that that the dispersion in ucnertainty seems consistent over time.

Another prediction from FIRE is that there is unambigous uncertainty reduction as one appraoches to the date of realization. Figure \ref{RevisionHist} plots the average revision in forecasts and uncertainty. The the more negative the revision lies in, the more rational of the forecast.

@@

\begin{figure}[h]\label{RevisionHist}
	\centering
	\includegraphics[width=6cm]{figures/PRCCPIMeanRev_hist.png} 
	\includegraphics[width=6cm]{figures/PRCCPIVarRev_hist.png}  \\
	\smallskip
	\includegraphics[width=6cm]{figures/PRCPCEMeanRev_hist.png} 
	\includegraphics[width=6cm]{figures/PRCPCEVarRev_hist.png}  \\
	\smallskip
		\includegraphics[width=6cm]{figures/SCEMeanRev_hist.png} 
	\includegraphics[width=6cm]{figures/SCEVarRev_hist.png}  \\
	\caption{Distribution of Revision in Uncertainty}
\end{figure}
